\thesistitle

### 2019-08-23 sections/results.tex
Link appendix

\subsection{Location}
Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different locations (see Section~\ref{sec:setuplocation}).
\begin{table}[H]
\centering
\begin{tabular}{@{}lrr@{}}
\toprule
Category & Clone instances & \% \\ \midrule
Method Level & 232,545 & 78.43\% \\
Class Level & 50,402 & 17.00\% \\
Constructor Level & 10,039 & 3.39\% \\
Interface Level & 2,693 & 0.91\% \\
Enum Level & 788 & 0.27\% \\
\end{tabular}
\caption{Amount of clone instances with a certain location} % Sander: miss: Amount of clone instances per location category ofzoiets
\label{tab:location}
\end{table}

@@

\subsection{Parameters}
Fig.~\ref{fig:arguments} shows how an increase in parameters lowers the maintainability of the refactored code. On the primary x-axis, the maintainability is displayed. The secondary x-axis shows the number of refactorings. The y-axis shows the number of parameters.

>>>>

\subsection{Location}
Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different locations (see Section~\ref{sec:setuplocation}).
\begin{table}[H]
\centering
\begin{tabular}{@{}lrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Clone instances}} & \textit{\textbf{\%}} \\ \midrule
Method Level & 232,545 & 78.43\% \\
Class Level & 50,402 & 17.00\% \\
Constructor Level & 10,039 & 3.39\% \\
Interface Level & 2,693 & 0.91\% \\
Enum Level & 788 & 0.27\% \\
\end{tabular}
\caption{Amount of clone instances with a certain location} % Sander: miss: Amount of clone instances per location category ofzoiets
\label{tab:location}
\end{table}

@@

\subsection{Parameters}
Fig.~\ref{fig:arguments} shows how an increase in parameters lowers the maintainability of the refactored code. On the primary x-axis, the maintainability is displayed. The secondary x-axis shows the number of refactorings. The y-axis shows the number of parameters. The table containing all underlying data and separate metrics is displayed in Appendix~\ref{sec:parameterstable}.
